Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.tex

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

The methionine cycle, illustrated in
Figure~\ref{fig-methionine-reactions}, is a fundamental pathway in human
metabolism, whose intermediate metabolites participate in a variety of
mechanisms which must compete for the same resources. Due to this
competition, as well as the fact that all the functions occur
simultaneously, the methionine cycle is highly regulated, with 6 known
allosteric effectors (REFERENCE). This complex regulation means that
quantitative modelling of the methionine cycle requires a detailed
kinetic model: this is why we chose it as a case study for Maud.

>>>>

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

The methionine cycle, illustrated in
Figure~\ref{fig-methionine-reactions}, is a fundamental pathway in human
metabolism, whose intermediate metabolites participate in a variety of
mechanisms which must compete for the same resources. Due to this
competition, as well as the fact that all the functions occur
simultaneously, the methionine cycle is highly regulated, with 6 known
allosteric effectors
\citep{martinov2000, nijhout2006, korendyaseva_allosteric_2008}. This
complex regulation means that quantitative modelling of the methionine
cycle requires a detailed kinetic model: this is why we chose it as a
case study for Maud.
